### 2020-04-14 serial.tex
more progress

>>>>

We use a simulation-based approach to compare the estimates of $\mathcal R$ based on the serial- and generation-interval distributions. 
To do so, we model the intrinsic generation-interval distribution and the incubation period using a multivariate log-normal distribution with log means $\mu_G, \mu_I$, log standard variances $\sigma_G^2, \sigma_I^2$, and correlation $\rho$.
The multivariate log-normal distribution is parameterized based on pameter estimates for COVID-19.
We construct the forward serial-interval distribution during the exponential growth period as follows:
\begin{equation}
S_i = -B_i + (G_i|B_i) + I_i,
\end{equation}
where the backward incubation period $B_i$ of an infector is simulated by drawing random log-normal samples $A_i$ with log mean $\mu_I$ and log variance $\sigma_I^2$ and resampling $A_i$, each weighted by the inverse of the exponential growth function $\exp(-rA_i)$;
the intrinsic generation interval conditional on the incubation period of the infector $(G_i|B_i)$ is drawn from a log-normal distribution with log mean $\mu_G + \sigma_G \rho (\log(B_i) - \mu_I)/\sigma_I$ and log variance $\sigma_G^2 (1-\rho^2)$;
the forward incubation period $I_i$ of an infectee is drawn from a log-normal distribution with log mean $\mu_I$ and log variance $\sigma_I^2$.
We then calculate the reproduction number $\mathcal R$ using the empirical estimator:
\begin{equation}
\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r S_i)}.
\end{equation}
We compare this estimate with a naive estimate of $\mathcal R$ that assumes that the backward and the forward incubation periods are identically distributed:
\begin{equation}
\mathcal R = \frac{1}{\frac{1}{N}\sum_{i=1}^N \exp(- r T_i)},
\end{equation}
where
\begin{equation}
T_i = -A_i + (G_i|A_i) + I_i.
\end{equation}
